---
title: "RecipeRecommender"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RecipeRecommender}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction 
This package provied a environment to the well-known [Spoonacular](spoonacular.com) website. This website provides all kinds of information about food, nutrition and everything connected to it. 

# Prerequisites 
Before looking at the code one must set up an application on [RapidAPI](rapidapi.com/) in order to receive a token and beeing able to access the data.

[Spoonacular](spoonacular.com) only provides a freemium API, so be careful with the amount of data requested. 

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
load(file="data/sample_data.RData")
```

```{r setup, eval=FALSE}
library(RecipeRecommender)
```

# Core Functionalities
### Recommendations
Given a list of ingredients the first package function can return a certain number of recipe recommendations. 

```{r recommendations, eval=FALSE}
get_recommendations(list("beer", "deer"), 10, your_key)
```

### Recipe Summary
Then, once one decided which the prefered recipe is, it is possible to get the summary of the recipe of choice. 

```{r summary, eval=FALSE}
get_recipe("985221", your_key)
```
